---
title: "HW10"
author: "Jiarui Chang"
date: "2020/11/28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(survival)
```

## 1
```{r}
Data <- cancer
Data$Age_group <- ifelse(Data$age < 65, "Young", "Old")
fit <- coxph(Surv(time, status) ~ Age_group, data = Data)
summary(fit)
```
\
From the result we can find that the hazard rate for old relative to young is $e^{-0.2985}$.
\


## 2
```{r}
prop <- cox.zph(fit)
prop
plot(prop)
```
\
From the plot we can find that the p-value is much more greater than 0.05, and the line in the plot is not a straight line, thus the proportional hazards assumption fail to hold in this situation.
\


## 3
```{r}
Data$sex_group <- ifelse(Data$sex == 1, "Male", "Female")
fit2 <- coxph(Surv(time, status) ~ sex_group, data = Data)
summary(fit2)
```
```{r}
prop2 <- cox.zph(fit2)
prop2
plot(prop2)
```
\
From the result we can see that the assumption for proportional hazards assumption hold in this situation, thus we can build a cox proportaional model by using sex_group.
\


```{r}
fit3 <- coxph(Surv(time, status) ~ Age_group + sex_group, data = Data)
summary(fit3)
```

```{r}
prop3 <- cox.zph(fit3)
plot(prop3)
```





