---
title: "HW5"
author: "Jiarui Chang"
date: "2020/10/15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,warning=F,message=F}
library(dplyr)
library(emmeans)
```

## 1
# a
```{r}
chicken <- ChickWeight %>% filter(Time == 21)
fit <- lm(weight ~ Diet, data = chicken)
summary(aov(fit))
```
\
From the result we can find out that the p-value of F test is 0.00686, much more smaller than 0.05, thus we can reject the null hypothesis. Conclude that there is a significant difference between mean weight among 4 groups.
\

# b
```{r}
birthweright <- ChickWeight %>% filter(Time == 0)
adjust_weight <- chicken %>% left_join(birthweright, by = "Chick")
adjust_weight <- adjust_weight$weight.x - adjust_weight$weight.y 
chicken["weight"] <- adjust_weight
fit2 <- lm(weight~Diet, data = chicken)
summary(aov(fit2))
ls <- lsmeans(fit2, ~Diet)
ls
```
\
After we adjust the weight by the birth weight, we can find out the p-value 0.00627 is still less than 0.05, so there is a significant difference between mean of 4 groups. The Lsmean is shown above.

## 2
# ab
```{r}
result_1 <- pairwise.t.test(chicken[['weight']], chicken[['Diet']], p.adjust.method = "bonferroni")
result_2 <- TukeyHSD(aov(fit))
result_1
result_2
```
\
From the result above we can find out that 
\

## 3

```{r}
kruskal.test(weight~Diet, data = chicken)
```