---
title: "HW7"
author: "Jiarui Chang"
date: "2020/11/4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1
# a
```{r, message=F,warning = F}
library(dplyr)
library(glmnet)
```
```{r}
day21 <- ChickWeight %>% filter(Time == 21)
day21_withoutad <- day21 %>% mutate(WeightGroup = ifelse(weight < 120,1,0))
day21_withoutad_14 <- day21_withoutad %>% filter(Diet %in% c(1,4))
logit_result <- glm(WeightGroup ~ Diet, data = day21_withoutad_14,
                    family = "binomial")
summary(logit_result)
```
\
From the result above we can find out the p-value for $\beta_1$ is much larger than 0.05, we fail to reject the null hypothesis. and conclude that there is no significant association between group diet 1 and diet 4 without adjustment for birthweight.
\

# b

```{r}
birth_weight <- ChickWeight %>% filter(Time == 0)
day21_withad <- day21 %>% left_join(birth_weight, by = ("Chick")) %>%
  mutate(ad_weight = weight.x - weight.y) %>% select(ad_weight, Time.x, Chick, Diet.x)
colnames(day21_withad) <- c("AdjustWeight", "Time", 
                               "Chick", "Diet")
day21_withad <- day21_withad %>% mutate(WeightGroup = ifelse(AdjustWeight < 120,1,0))
day21_withad_14 <- day21_withad %>% filter(Diet %in% c(1,4))
logit_result2 <- glm(WeightGroup ~ Diet, data = day21_withad_14,
                     family = "binomial")
summary(logit_result2)
```
\
From the result above we can find out the p-value for $\beta_1$ is much larger than 0.05, we fail to reject the null hypothesis. and conclude that there is no significant association between group diet 1 and diet 4 with adjustment for birthweight.
\

## 2
# a
```{r}
logit_result3 <- glm(WeightGroup ~ Diet, data = day21_withoutad,
                     family = "binomial")
summary(logit_result3)
```
\
From the result above we can find out the p-value for $\beta_1$, $\beta_2$, $\beta_3$ are much larger than 0.05, we fail to reject the null hypothesis. and conclude that there is no significant association between group diet 1, diet2, diet 3 and diet 4 without adjustment for birthweight.
\

# b
```{r}
logit_result4 <- glm(WeightGroup ~ Diet, data = day21_withad,
                     family = "binomial")
summary(logit_result4)
```
\
From the result above we can find out the p-value for $\beta_1$, $\beta_2$, $\beta_3$ are much larger than 0.05, we fail to reject the null hypothesis. and conclude that there is no significant association between group diet 1, diet2, diet 3 and diet 4 without adjustment for birthweight.
\

## 3
```{r,warning=F}
set.seed(10)
diet1 <- cbind(1, as.numeric(day21_withoutad_14$Diet))
cv1 <- cv.glmnet(diet1, day21_withoutad_14$WeightGroup, family = "binomial")
plot(cv1)
```

```{r,warning=FALSE}
fit1 <- glmnet(diet1, day21_withoutad_14$WeightGroup, family = "binomial", lambda = cv1$lambda.min)
coef(cv1, s = "lambda.min")
summary(fit1$beta)
cv1
```

```{r,warning=F}
diet2 <- cbind(1, as.numeric(day21_withad_14$Diet))
cv2 <- cv.glmnet(diet2, day21_withad_14$WeightGroup, family = "binomial")
plot(cv2)
```

```{r}
fit2 <- glmnet(diet2, day21_withad_14$WeightGroup, family = "binomial", lambda = cv2$lambda.min)
coef(cv2, s = "lambda.min")
cv2
```
