---
title: "HW8"
author: "Jiarui Chang"
date: "2020/11/9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,message=F,warning=F}
library(glmnet)
```
## 1
# a
```{R}
dataset <- Sleuth3::ex2224
as_factor <- function(x){
  as.factor(as.numeric(x))
}
for (i in 1:5){
  dataset[,i] = as_factor(dataset[,i])
}

```

```{r}
fit1 <- glm(Failures ~Operator, data = dataset, family = poisson)
summary(fit1)
```

```{r}
anova(fit1, test = "Chisq")
```
\
From the result we can find out the p value is significant, thus we can condlude there is a significant association. 
\

# b 
```{r}
fit2 <- glm(Failures ~ System + Operator + Valve + Size + Mode, data = dataset, family = poisson, offset = log(Time))
summary(fit2)
```

```{r}
anova(fit2, test = "Chisq")
```
\
From the result we can find out the p value is significant, thus we can condlude there is a significant association between Faliures, System, Valve and Size. 
\


## 2
# a
From the result of fit1 model, we can conclude that operator 2 will reduce the mean number of failures by 0.54. Operator 3 will reduce the mean number of failures by 0.34. Operator 4 will reduce the mean number of failures by 0.82. And from the summary result, only the operator 3 and operator 4 are significant.
\
\
From the result of fit2 model, we can conclude that systme 2 will increase the mean number of failures by 1.5. System 3 wll increase the mean number of failures by 1.76. System 4 will increase the mean number of failures by 2.4. System 5 will increase the mean number of failures by 0.4. Operator 2 will increase the mena number of failures by 1.02. Operator 3 will reduce the mean number of failures by 0.7. Operator 4 will reduce the mean number of failures by 0.92. Valve 2 will will increase the mean number of failures by 0.203. Valve 3 will increase the mean number of failures 0.834. Valve 4 will reduce the mean number of failures by 18.28. Valve 5 will increase the mean number of failures 5. Valve 6 will increase the mean number of failures 1.74. Size 2 will reduce mean number of failures by 0.0121. Size 3 will increase mean of failures by 4. And from the summary result, system3, system4, operator3, operator4, valve4, valve5, size3 are significant.


# b
```{r}
pchisq(fit1$deviance, fit1$df.residual, lower.tail=FALSE)
```

```{r}
pchisq(fit2$deviance, fit2$df.residual, lower.tail=FALSE)
```
\
We can find out that both of the two model has a really small p-value, thus we can reject the null hypothesis.
\

## 3
```{r}
set.seed(1)
mat <- model.matrix(Failures ~ System + Operator + Valve + Size + Mode, dataset)[,-1]
x <- as.matrix(mat)
cv <- cv.glmnet(x, dataset$Failures, family="poisson", offset = log(dataset$Time))
plot(cv)
```
```{r}
cv$lambda.min
coef(cv, cv$lambda.min)
```
\
Based on the result, the model would only contain system 2 to 5, operator 2 to 4, valve 2, 4, 5 and size 3 with the value showed above. 
\

















